Supplementary Appendix

### 2025-02-18 docs/manuscript_GNM.qmd
supp should work now

@@

### Registration and Reporting

We pre-registered our predictions, methods and planned analysis prior to data exploration and analysis [@dimri2024]. We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (in @supptbl-1). All resources associated with this study, including data and code, are available at <https://github.com/shreyadimri/Green_Nest_Material> (insert Zenodo citation later).

### Systematic Review

@@

We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022 @supptbl-2

#### ility criteria

@@

@@

<summary>Supplementary Appendix</summary>

>>>>

```{r Setup, include=FALSE, echo=FALSE}

pacman::p_load(readr)

```

@@

Registration and Reporting

We pre-registered our predictions, methods and planned analysis prior to data exploration and analysis [@dimri2024]. We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (in @figsupp-checklist). All resources associated with this study, including data and code, are available at \[<https://github.com/shreyadimri/Green_Nest_Material>\] (insert Zenodo citation later).

## Systematic Review

### Literature search

```{r load search data, include=FALSE, echo=FALSE}

unique_reference_list <- read_csv("data/unique_reference_list.csv")

```

We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022 and updated it on 12.08.2024. The search query was designed in three blocks to included terms for predictor/treatment ("green*" OR "herb*" OR "aromatic*" AND "nest*"), population of interest ("bird*" OR "aves" OR "avian" OR "ornithol*" OR "passerine*" OR "passeriform*" OR "songbird*" OR list of all bird genera) and only experimental studies ("experiment*" OR "manipulat\*") (for complete search string details see @figsupp-string). We searched the title, abstract and keywords in English language only. Our search found `{r} nrow(unique_reference_list)`

@@

We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022

Eligibility criteria

@@

## Supplementary Appendix

@@

<summary>Supplementary materials</summary>

### 2025-02-18 docs/supplementary_appendix.qmd
supp should work now

---
title: "Supplementary Appendix"
---

::: {#supptbl-1}
## PRISMA Eco-Evo Checklist

| Col1 | Col2 | Col3 |
|------|------|------|
|      |      |      |
|      |      |      |
|      |      |      |

Here is a Prisma list that we have filled according to
:::

::: {#supptbl-2}
## Search String

The search was conducted twice, the first time on 07.09.2022 and then repeated on 12.08.2024 to ensure it was the most up to date and did not miss any additional articles on the topic that were published meanwhile. For both the searches, we did not use any time limitation i.e. it included all the published literature till that given date. We used **Advance Search** option for both Web of Science Core Collection Database and Scopus Database using the search query given below.

1.  **Web of Science Core Collection Database**

Databases used in the search:

-   Science Citation Index Expanded (SCI-EXPANDED) - 1900 - present

-   Social Sciences Citation Index (SSCI) -1900 - present

-   Arts & Humanities Citation Index (AHCI) - 1975 - present

-   Conference Proceedings Citation Index - Science (CPCI-S) -1991 - present

-   Conference Proceedings Citation Index - Social Science & Humanities (CPCI-SSH) -1991 - present

-   Emerging Sources Citation Index (ESCI) 2017- present

>>>>

---
title: "Supplementary Appendix"
bibliography: references.bib
---

::: {#figsupp-checklist}
| Checklist Item | Sub-item Number | Sub-item | Reported by authors? | Notes |
|----------------|-----------------|----------|----------------------|-------|
|                |                 |          |                      |       |
|                |                 |          |                      |       |
|                |                 |          |                      |       |

Prisma Eco-Evo Checklist @odea2021
:::

::: {#figsupp-string}
The search was conducted twice, the first time on 07.09.2022 and then repeated on 12.08.2024 to ensure it was the most up to date and did not miss any additional articles on the topic that were published meanwhile. For both the searches, we did not use any time limitation i.e. it included all the published literature till that given date. We used **Advance Search** option for both Web of Science Core Collection Database and Scopus Database using the search query given below.
:::
